---
output:
  html_document:
    fig_caption: yes
    fig_height: 2.5
    fig_width: 4
    highlight: zenburn
    toc: yes
---

```{r setup, include=FALSE, cache=FALSE}
library(knitr)
# set global chunk options
opts_chunk$set(fig.path='figure/minimal-', fig.align='center', fig.show='hold', fig.height=2.5, fig.width=4, figerror=TRUE, plotly=TRUE, error=TRUE)
```


# Plotly, ggplot2, and R
[Plotly](http://www.plot.ly) is a cool, open-source project  ( [github](https://github.com/plotly) ) to help people get interactive plots online easily through a number of various programming languages. This page serves as a guide to using it with [R's](http://www.r-project.org/) [ggplot2](http://ggplot2.org/) visualization and plotting package and will be updated as support for new geoms (ggplot plots/visualization types) are added.

Most examples will be taken straight from [ggplot's docs website](http://docs.ggplot2.org/current/). The master list of geoms is at the botttom of this post. Some of the plots have minor errors.

## Installing Plot.ly
Installing Plot.ly within R is easy. 

```{r, plotly=TRUE, eval=FALSE} 
#autoloads ggplot
library(devtools)
install_github("plotly", "ropensci")
signup("yourusername", "youremail@foo.bar")
```

```{r, echo=FALSE}
plotly.key = 'h4lbm5pbfx'

```

```{r}
library(plotly)
py <- plotly(username= 'xysmas', key=plotly.key)
```

# On With the Plots

## geom_abline, hline, vline

```{r lines}
coefs <- coef(lm(Sepal.Length ~ Petal.Width, data = iris))
p.iris <- ggplot(iris, aes(Petal.Width, Sepal.Length, color = Species))
p.iris <- p.iris + geom_point()
p.iris.hline <- p.iris + geom_hline(yintercept=7)
p.iris.abline <- p.iris + geom_abline(intercept=coefs[1], slope=coefs[2], colour="red", size=2)
p.iris.vline <- p.iris + geom_vline(xintercept=2)
p.iris.abline
p.iris.hline
p.iris.vline
```

```{r figerror=TRUE}
py$ggplotly(p.iris.abline)
# odd little error
py$ggplotly(p.iris.hline)
# odd little error
py$ggplotly(p.iris.vline)
```
geom_abline doesn't work. 




##  geom_jitter
```{r jitter}
p <- ggplot(iris, aes(Petal.Width, Sepal.Length, color = Species))
p + geom_jitter()
py$ggplotly(p+geom_jitter())
#try position instead
py$ggplotly(p + geom_point(position=position_jitter()))

```
geom_jitter fails, but position jitter passed to geompoint seems to work fine. 

## geom_line
(potentially the most useless plot ever, but just as an example...)
```{r line}
p <- p + geom_line()
p
```

```{r}
py$ggplotly(p)
```
yes, funny that abline and the other line geoms do not work.


## geom_path

```{r paths}
#  Use the arrow parameter to add an arrow to the line
# See ?grid::arrow for more details
library(grid)
c <- ggplot(economics, aes(x = date, y = pop))
# Arrow defaults to "last"
c + geom_path(arrow = arrow())
py$ggplotly(c + geom_path(arrow = arrow()))
```

## geom_point
Clearly this works.


## geom_polygon
```{r poly}
### example straight from ggplot2
# When using geom_polygon, you will typically need two data frames:
# one contains the coordinates of each polygon (positions),  and the
# other the values associated with each polygon (values).  An id
# variable links the two together

ids <- factor(c("1.1", "2.1", "1.2", "2.2", "1.3", "2.3"))

values <- data.frame(
  id = ids,
  value = c(3, 3.1, 3.1, 3.2, 3.15, 3.5)
)

positions <- data.frame(
  id = rep(ids, each = 4),
  x = c(2, 1, 1.1, 2.2, 1, 0, 0.3, 1.1, 2.2, 1.1, 1.2, 2.5, 1.1, 0.3,
  0.5, 1.2, 2.5, 1.2, 1.3, 2.7, 1.2, 0.5, 0.6, 1.3),
  y = c(-0.5, 0, 1, 0.5, 0, 0.5, 1.5, 1, 0.5, 1, 2.1, 1.7, 1, 1.5,
  2.2, 2.1, 1.7, 2.1, 3.2, 2.8, 2.1, 2.2, 3.3, 3.2)
)

# Currently we need to manually merge the two together
datapoly <- merge(values, positions, by=c("id"))

(p <- ggplot(datapoly, aes(x=x, y=y)) + geom_polygon(aes(fill=value, group=id)))
py$ggplotly(p)
rm(p)
```


## geom_ribbon
```{r ribbon}
msamp <- movies[sample(nrow(movies), 1000), ]
m <- ggplot(msamp, aes(y=log(votes), x=year))
m <- m + geom_point()
m <- m + stat_summary(geom="ribbon", fun.ymin="min", fun.ymax="max")
m
py$ggplotly(m)

```

Points work, stat summary doesn't. 


## geom_segment
example from ggplot docs
```{r seg}
library(grid) # needed for arrow function
p <- ggplot(seals, aes(x = long, y = lat))
p <- p + geom_segment(aes(xend = long + delta_long, yend = lat + delta_lat), arrow = arrow(length = unit(0.1,"cm")))
p
py$ggplotly(p)
```


# master list of geoms:
[ggplot2 docs](http://docs.ggplot2.org/current/)

### geoms
* geom_abline() = FALSE
* geom_area() = FALSE
* geom_bar() = FALSE
* geom_bin2d() = FALSE
* geom_blank() = 
* geom_boxplot() = FALSE
* geom_contour() = FALSE
* geom_crossbar() = FALSE
* geom_density() = FALSE
* geom_density2d() = FALSE
* geom_dotplot() = FALSE
* geom_errorbar() = FALSE
* geom_errorbarh() = FALSE
* geom_freqpoly() = FALSE
* geom_hex() = Untested
* geom_histogram() = FALSE
* geom_hline() = FALSE
* geom_jitter() = FALSE
* geom_line() = TRUE
* geom_linerange() = FALSE
* geom_map() = FALSE
* geom_path() = TRUE
* geom_point() = TRUE
* geom_pointrange() = FALSE
* geom_polygon() =TRUE 
* geom_quantile() = FALSE
* geom_raster() = FALSE
* geom_rect() = FALSE
* geom_ribbon() = FALSE
* geom_rug() = FALSE
* geom_segment() = TRUE
* geom_smooth() = FALSE
* geom_step() = FALSE
* geom_text() = FALSE
* geom_tile() = FALSE
* geom_violin() = FALSE
* geom_vline() = FALSE

### stats 
* stat_abline() = FALSE
* stat_bin()
* stat_bin2d()
* stat_bindot()
* stat_bindot()
* stat_binhex()
* stat_contour()
* stat_density()
* stat_density2d()
* stat_ecdf()
* stat_function()
* stat_hline()
* stat_identity()
* stat_qq()
* stat_quantile() = false
* stat_smooth()
* stat_spoke()
* stat_sum()
* stat_summary()
* stat_summary_hex()
* stat_summary2d()
* stat_unique()
* stat_vline()
* stat_ydensity()

### other ggplot stuff
* expand_limits
* guide_legend
* guide_colourbar(guide_colorbar)
* scale_alpha(scale_alpha_continuous, scale_alpha_discrete)
* scale_area()
* scale_color_brewer
* scale_color_continuous
* scale_color_discrete
* scale_color_gradient
* scale_color_gradient2
* scale_color_gradientn

* coord_cartesian
* coord_equal
* coord_fixed
* coord_flip
* coord_map = FALSE
* coord_polar
* coord_trans
* 
* facet_grid
* facet_null
* facet_wrap
* 
* position_dodge
* position_fill
* position_identity
* position_jitter
* position_stack



