
```{r setup, include=FALSE, cache=FALSE}
library(knitr)
# set global chunk options
opts_chunk$set(fig.path='figure/minimal-', fig.align='center', fig.show='hold', error=TRUE, plotly=TRUE)
```

```{r, echo=FALSE}
plotly.key = 'h4lbm5pbfx'

```
```{r test, echo=FALSE}
a <- "ihateyou"
a
```


# Plotly and geoms
I'm going to test out different ggplot geoms to check for compatibility.  Most examples will be taken straight from ggplots website.

Let's load / install the package and get my plotly key: 

```{r, plotly=TRUE} 
#autoloads ggplot
# library("devtools")
# install_github("plotly", "ropensci")
library(plotly)
# signup("xysmas", "xysmas@gmail.com")
py <- plotly(username= 'xysmas', key=plotly.key)
```


# the plots

## geom_abline, hline, vline

```{r lines}
coefs <- coef(lm(Sepal.Length ~ Petal.Width, data = iris))
p.iris <- ggplot(iris, aes(Petal.Width, Sepal.Length, color = Species))
p.iris <- p.iris + geom_point()
p.iris.hline <- p.iris + geom_hline(yintercept=7)
p.iris.abline <- p.iris + geom_abline(intercept=coefs[1], slope=coefs[2], colour="red", size=2)
p.iris.vline <- p.iris + geom_vline(xintercept=2)
p.iris.abline
p.iris.hline
p.iris.vline
```

```{r}
py$ggplotly(p.iris.abline)
# odd little error
py$ggplotly(p.iris.hline)
# odd little error
py$ggplotly(p.iris.vline)
```
geom_abline doesn't work. 

## geom_area
```{r}
# Generate data
huron <- data.frame(year = 1875:1972, level = as.vector(LakeHuron))
library(plyr) # to access round_any
huron$decade <- round_any(huron$year, 10, floor)

h <- ggplot(huron, aes(x=year))
h <- h + geom_area(aes(y = level))
h
```

```{r}
py$ggplotly(h)
```
geom_area = FALSE!

## geom_bar
```{r bar}
bar <- ggplot(iris, aes(Species, colour=Species, fill=Species))
bar <- bar + geom_bar()
bar
```

```{r barpy}
py$ggplotly(bar)
```

Nope.

## geom_bin2d
```{r bin}
d <- ggplot(diamonds, aes(x = x, y = y)) + xlim(4,10) + ylim(4,10)
d <- d + geom_bin2d()
py$ggplotly(d)
```

Nope. 

## geom_boxplot
```{r boxplot}
p.iris <- ggplot(iris, aes(Species, Sepal.Length, fill=Species))
p.iris <- p.iris + geom_boxplot()
py$ggplotly(p.iris)
```

Nope. 


## geom_contour
```{r}
library(reshape2)
volcano3d <- melt(volcano)
colnames(volcano3d) <- c("x", "y", "z")
p <- ggplot(volcano3d, aes(x, y, z = z)) +  geom_contour()
py$ggplotly(p)
```

Nope.

## geom_crossbar, linerange, pointrange, and errorbar
```{r crossbar}
# From ggplot example:
# Generate data: means and standard errors of means for prices
# for each type of cut
dmod <- lm(price ~ cut, data=diamonds)
cuts <- data.frame(cut=unique(diamonds$cut), predict(dmod, data.frame(cut = unique(diamonds$cut)), se=TRUE)[c("fit","se.fit")])
# Display estimates and standard errors in various ways
se <- ggplot(cuts, aes(cut, fit,
  ymin = fit - se.fit, ymax=fit + se.fit, colour = cut))
se + geom_linerange()
se + geom_pointrange()
se + geom_crossbar()
py$ggplotly(se+geom_linerange())
py$ggplotly(se+geom_pointrange())
py$ggplotly(se+geom_crossbar())
py$ggplotly(se+geom_errorbar())
```

Nope. 

## geom_density/2d
```{r density}
p <- ggplot(iris, aes(Sepal.Width, fill=Species, group=Species))
p + geom_density(alpha=0.5)
py$ggplotly(p + geom_density(alpha=0.5))
```
nope.

## geom_dotplot
```{r dotplot}
p + geom_dotplot(binwidth=0.1)
py$ggplotly(p + geom_dotplot(binwidth=0.1))
```
no. 


## geom_freqpoly

```{r freqpoly}
p + geom_freqpoly()
py$ggplotly(p + geom_freqpoly())
```
no. 

## geom_hex
```{r hex}
p <- ggplot(iris, aes(Sepal.Width, Petal.Length, fill=Species, group=Species))
p + geom_hex()

```


## geom_histogram
```{r hist}
p <- ggplot(iris, aes(Sepal.Width, fill=Species, group = Species))
p + geom_histogram()
py$ggplotly(p+geom_histogram())
```
no.


##  geom_jitter
```{r jitter}
p <- ggplot(iris, aes(Petal.Width, Sepal.Length, color = Species))
p + geom_jitter()
py$ggplotly(p+geom_jitter())
#try position instead
py$ggplotly(p + geom_point(position=position_jitter()))

```
geom_jitter fails, but position jitter passed to geompoint seems to work fine. 

## geom_line
(potentially the most useless plot ever, but just as an example...)
```{r line}
p <- p + geom_line()
p
```

```{r}
py$ggplotly(p)

```
yes, funny that abline and the other line geoms do not work.

## geom_map 
straight from ggplot docs:
```{r maps}
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
library(reshape2) # for melt
library(maps)
crimesm <- melt(crimes, id = 1)
  states_map <- map_data("state")
  crimemap <- ggplot(crimes, aes(map_id = state)) +
    geom_map(aes(fill = Murder), map = states_map) + 
    expand_limits(x = states_map$long, y = states_map$lat)

  crimemap.coordmap <- last_plot() + coord_map()
  
  crimemap.facet <- ggplot(crimesm, aes(map_id = state)) + 
    geom_map(aes(fill = value), map = states_map) + 
    expand_limits(x = states_map$long, y = states_map$lat) + 
    facet_wrap( ~ variable)


# When using geom_polygon, you will typically need two data frames:
# one contains the coordinates of each polygon (positions),  and the
# other the values associated with each polygon (values).  An id
# variable links the two together

ids <- factor(c("1.1", "2.1", "1.2", "2.2", "1.3", "2.3"))

values <- data.frame(
  id = ids,
  value = c(3, 3.1, 3.1, 3.2, 3.15, 3.5)
)

positions <- data.frame(
  id = rep(ids, each = 4),
  x = c(2, 1, 1.1, 2.2, 1, 0, 0.3, 1.1, 2.2, 1.1, 1.2, 2.5, 1.1, 0.3,
  0.5, 1.2, 2.5, 1.2, 1.3, 2.7, 1.2, 0.5, 0.6, 1.3),
  y = c(-0.5, 0, 1, 0.5, 0, 0.5, 1.5, 1, 0.5, 1, 2.1, 1.7, 1, 1.5,
  2.2, 2.1, 1.7, 2.1, 3.2, 2.8, 2.1, 2.2, 3.3, 3.2)
)

test<-ggplot(values) + geom_map(aes(map_id = id), map = positions) +
  expand_limits(positions)

```

```{r crimemap}
py$ggplotly(test)
py$ggplotly(crimemap.facet)
py$ggplotly(ggplot(crimes, aes(map_id = state)) +
    geom_map(aes(fill = Murder), map = states_map) + 
    expand_limits(x = states_map$long, y = states_map$lat))
```
no maps.


## geom_path

```{r paths}
#  Use the arrow parameter to add an arrow to the line
# See ?grid::arrow for more details
library(grid)
c <- ggplot(economics, aes(x = date, y = pop))
# Arrow defaults to "last"
c + geom_path(arrow = arrow())
py$ggplotly(c + geom_path(arrow = arrow()))
```
success!

## geom_point
Clearly this works.


## geom_polygon
I"m guessing that since the map, which uses polygon, didn't work, this probably won't either. Stolen example from ggplot docs. 
```{r poly}
# When using geom_polygon, you will typically need two data frames:
# one contains the coordinates of each polygon (positions),  and the
# other the values associated with each polygon (values).  An id
# variable links the two together

ids <- factor(c("1.1", "2.1", "1.2", "2.2", "1.3", "2.3"))

values <- data.frame(
  id = ids,
  value = c(3, 3.1, 3.1, 3.2, 3.15, 3.5)
)

positions <- data.frame(
  id = rep(ids, each = 4),
  x = c(2, 1, 1.1, 2.2, 1, 0, 0.3, 1.1, 2.2, 1.1, 1.2, 2.5, 1.1, 0.3,
  0.5, 1.2, 2.5, 1.2, 1.3, 2.7, 1.2, 0.5, 0.6, 1.3),
  y = c(-0.5, 0, 1, 0.5, 0, 0.5, 1.5, 1, 0.5, 1, 2.1, 1.7, 1, 1.5,
  2.2, 2.1, 1.7, 2.1, 3.2, 2.8, 2.1, 2.2, 3.3, 3.2)
)

# Currently we need to manually merge the two together
datapoly <- merge(values, positions, by=c("id"))

(p <- ggplot(datapoly, aes(x=x, y=y)) + geom_polygon(aes(fill=value, group=id)))
py$ggplotly(p)
```

Wrong, it works.

##geom_quantile /stat_quantile
```{r quant}
msamp <- movies[sample(nrow(movies), 1000), ]
q10 <- seq(0.05, 0.95, by=0.05)
m <- ggplot(msamp, aes(year, rating)) + geom_point()
m <- m + stat_quantile(aes(colour = ..quantile..), quantiles = q10) +
  scale_colour_gradient2(midpoint = 0.5)
m
py$ggplotly(m)
```
no. 


## geom_raster
Example taken from ggplot docs
```{r}
# Generate data
pp <- function (n,r=4) {
 x <- seq(-r*pi, r*pi, len=n)
 df <- expand.grid(x=x, y=x)
 df$r <- sqrt(df$x^2 + df$y^2)
 df$z <- cos(df$r^2)*exp(-df$r/6)
 df
}
raster <- qplot(x, y, data = pp(20), fill = z, geom = "raster")
raster
py$ggplotly(raster)
```
no. 

## geom_rect
```{r rect}
df <- data.frame(
  x = sample(10, 20, replace = TRUE),
  y = sample(10, 20, replace = TRUE)
)
p <- ggplot(df, aes(xmin = x, xmax = x + 1, ymin = y, ymax = y + 2)) 
p <- p + geom_rect()
p
py$ggplotly(p)
```

No. 

## geom_ribbon
```{r ribbon}
msamp <- movies[sample(nrow(movies), 1000), ]
m <- ggplot(msamp, aes(y=log(votes), x=year))
m <- m + geom_point()
m <- stat_summary(geom="ribbon", fun.ymin="min", fun.ymax="max")
m
py$ggplotly(m)

```

Points work, stat summary doesn't. 

## geom_rug
```{r rug}
msamp <- movies[sample(nrow(movies), 1000), ]
p <- ggplot(msamp, aes(year, log(votes)))
p <- p + geom_point()
(p <- p + geom_rug())
py$ggplotly(p)

```

No.

## geom_segment
example from ggplot docs
```{r seg}
library(grid) # needed for arrow function
p <- ggplot(seals, aes(x = long, y = lat))
(p <- p + geom_segment(aes(xend = long + delta_long, yend = lat + delta_lat), arrow = arrow(length = unit(0.1,"cm"))))
py$ggplotly(p)
```
Yes - so you could use segment to recreate other charts, i suppose, ala this ggplot docs example:
```{r}
(p <- qplot(x, Freq, data = counts, geom = "segment",
  yend = 0, xend = x, size = I(10)))
py$ggplotly(p)
```

## geom_smooth
```{r}
p <- ggplot(mtcars, aes(wt, mpg, color = factor(cyl) ))
p <- p + geom_point()
p <- p + geom_smooth()
p
py$ggplotly(p)
```
No smoothing.


## geom_step
Example straight from ggplot docs
```{r step}
# Also works with other aesthetics
df <- data.frame(
  x = sort(rnorm(50)),
  trt = sample(c("a", "b"), 50, rep = TRUE)
)
p <- qplot(seq_along(x), x, data = df, geom="step", colour = trt)
p
py$ggplotly(p)
```

No.

## geom_text
```{r text}
p <- ggplot(iris, aes(Petal.Width, Sepal.Length, label=Species, colour=Species))
p <- p + geom_point()
p <- p + geom_text(angle=45)
p <- p + geom_text(data = NULL, x = 0.5, y = 7.2, label = "plotly is cool")
p
py$ggplotly(p)
```
No.


## geom_tile
```{r tile}
# Generate data
pp <- function (n,r=4) {
 x <- seq(-r*pi, r*pi, len=n)
 df <- expand.grid(x=x, y=x)
 df$r <- sqrt(df$x^2 + df$y^2)
 df$z <- cos(df$r^2)*exp(-df$r/6)
 df
}
p <- ggplot(pp(20), aes(x=x,y=y))
p <- p + geom_tile(aes(fill=z))
p
py$ggplotly(p)
```
No.

## geom_violin
```{r vio}
p <- ggplot(mtcars, aes(factor(cyl), wt, fill=factor(cyl)))
p <- p + geom_violin()
p
py$ggplotly(p)
```
No.




# master list of geoms:
[ggplot2 docs](http://docs.ggplot2.org/current/)

### geoms
* geom_abline() = FALSE
* geom_area() = FALSE
* geom_bar() = FALSE
* geom_bin2d() = FALSE
* geom_blank() = 
* geom_boxplot() = FALSE
* geom_contour() = FALSE
* geom_crossbar() = FALSE
* geom_density() = FALSE
* geom_density2d() = FALSE
* geom_dotplot() = FALSE
* geom_errorbar() = FALSE
* geom_errorbarh() = FALSE
* geom_freqpoly() = FALSE
* geom_hex() = 
* geom_histogram() = FALSE
* geom_hline() = FALSE
* geom_jitter() = FALSE
* geom_line() = TRUE
* geom_linerange() = FALSE
* geom_map() = FALSE
* geom_path() = TRUE
* geom_point() = TRUE
* geom_pointrange() = FALSE
* geom_polygon() =TRUE 
* geom_quantile() = FALSE
* geom_raster() = FALSE
* geom_rect() = FALSE
* geom_ribbon() = FALSE
* geom_rug() = FALSE
* geom_segment() = TRUE
* geom_smooth() = FALSE
* geom_step() = FALSE
* geom_text() = FALSE
* geom_tile() = FALSE
* geom_violin() = FALSE
* geom_vline() = FALSE
### stats 
* stat_abline() = FALSE
* stat_bin()
* stat_bin2d()
* stat_bindot()
* stat_bindot()
* stat_binhex()
* stat_contour()
* stat_density()
* stat_density2d()
* stat_ecdf()
* stat_function()
* stat_hline()
* stat_identity()
* stat_qq()
* stat_quantile() = false
* stat_smooth()
* stat_spoke()
* stat_sum()
* stat_summary()
* stat_summary_hex()
* stat_summary2d()
* stat_unique()
* stat_vline()
* stat_ydensity()





* expand_limits
* guide_legend
* guide_colourbar(guide_colorbar)
* scale_alpha(scale_alpha_continuous, scale_alpha_discrete)
* scale_area()
* scale_color_brewer
* scale_color_continuous
* scale_color_discrete
* scale_color_gradient
* scale_color_gradient2
* scale_color_gradientn

* coord_cartesian
* coord_equal
* coord_fixed
* coord_flip
* coord_map = FALSE
* coord_polar
* coord_trans
* 
* facet_grid
* facet_null
* facet_wrap
* 
* position_dodge
* position_fill
* position_identity
* position_jitter
* position_stack



